\section{Introduction}
\label{sec:intro}

Deepfake technology uses deep generative models to synthesise or manipulate
facial images and videos, posing serious challenges for digital trust and
media authenticity~\cite{goodfellow2014gan}.
Early GAN-based deepfakes were easily identifiable, but style-based
architectures such as StyleGAN2~\cite{karras2020stylegan2} now produce
synthetic faces that are perceptually indistinguishable from real photographs.

Two broad detection families have emerged.
\emph{Spatial-domain} methods apply CNNs directly to pixel-space images,
exploiting texture and structural inconsistencies introduced during
synthesis~\cite{rossler2019faceforensics}.
\emph{Frequency-domain} methods analyse the Fourier or DCT spectrum,
motivated by the observation that transposed-convolution upsampling layers
leave periodic spectral artefacts absent from natural
photographs~\cite{frank2020frequency,dzanic2020fourier,durall2019unmasking}.

This project sits at the intersection of both families.
The central hypothesis is:
\begin{quote}
\emph{A dual-branch model that jointly processes spatial (RGB) and spectral
(FFT) features outperforms either modality alone on StyleGAN2 face
detection.}
\end{quote}

Three experiments test this hypothesis:
\begin{enumerate}
  \item \textbf{RGB} — ResNet18~\cite{he2016resnet} fine-tuned from
    ImageNet on raw $224\!\times\!224$ face images.
  \item \textbf{FFT} — identical ResNet18 trained from scratch on
    per-channel log-magnitude FFT spectra.
  \item \textbf{Hybrid} — dual-branch architecture that late-fuses 512-d
    features from both branches through a two-layer classification head.
\end{enumerate}

All models are augmented with Grad-CAM~\cite{selvaraju2017gradcam}
visualisations for post-hoc explainability.

\noindent\textbf{Contributions:}
\begin{itemize}
  \item A clean, reproducible three-way comparison of RGB, FFT, and Hybrid
    deepfake detectors under identical training conditions.
  \item Empirical evidence that frequency cues alone are insufficient for
    StyleGAN2 detection at the scale studied, yet add measurable value in a
    late-fusion architecture (perfect recall).
  \item Per-model Grad-CAM visualisations that confirm semantically
    meaningful spatial attention.
\end{itemize}
